Articles of Association of London Hackspace Ltd.

### 2011-07-26 constitution/articles-body.tex
Make directors' conflict-of-interest rules in line with latest CC GD1

\item
  The charity's objects (``Objects'') are specifically restricted to
  the following:
  \begin{enumerate}
  \item
    to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
  \item
    to provide and maintain shared community workspace and equipment in London.
  \end{enumerate}

@@

@@

  \label{cls:income-property}
    The income and property of the charity shall be applied solely
    towards the promotion of the Objects.
    \label{scls:director-reimburse}
      A director is entitled to be reimbursed from the property of the
      charity or may pay out of such property reasonable expenses
      properly incurred by him or her when acting on behalf of the
      charity.
      A director may benefit from trustee indemnity insurance cover
      purchased at the charity's expense in accordance with, and subject
      to the conditions in, section 73F of the Charities Act 1993.
      A director may receive an indemnity from the charity in the
      circumstances specified in article \ref{cls:directors-indemnity}.
    None of the income or property of the charity may be paid or
    transferred directly or indirectly by way of dividend bonus or
    otherwise by way of profit to any member of the charity. This does
    not prevent a member who is not also a director receiving:
      a benefit from the charity in the capacity of a beneficiary of the
      charity;
      reasonable and proper remuneration for any goods or services
      supplied to the charity.
    \label{scls:directors-remuneration} No director or connected person
    may:
      buy any goods or services from the charity on terms preferential to
      those applicable to members of the public;
      sell goods, services, or any interest in land to the charity;
      be employed by, or receive any remuneration from, the charity;
      receive any other financial benefit from the charity; unless:
        the payment is permitted by article \ref{scls:directors-scope}; or
        the directors obtain the prior written approval of the Commission
        and fully comply with any procedures it prescribes. In this article
        a `financial benefit' means a benefit, direct or indirect, which is
        either money or has a monetary value.

@@

      The directors may arrange for the purchase, out of the funds of the
      charity, of insurance designed to indemnify the directors in
      accordance with the terms of, and subject to the conditions in,
      section 73F of the Charities Act 1993.

@@

  \item \label{goods}

@@

    In sub-clauses \ref{scls:director-reimburse} to \ref{goods}, ``charity'' shall include

@@

  \item \label{def-connected}
    In sub-clauses \ref{scls:directors-remuneration} to \ref{goods}, \ref{conflict-interest-loyalty},
    and \ref{directors-validity-void} ``connected person'' means:
      \label{art:connected-child} a child, parent, grandchild,
      grandparent, brother or sister of the director;
      \label{art:connected-spouse} the spouse or civil partner of the
      director or of any person falling within paragraph (i) above;
      \label{art:connected-business} a person carrying on business in
      partnership with the director or with any person falling within
      paragraph (i) or (ii) above;
      an institution which is controlled –
        by the director or any connected person falling within paragraph (i) to (iii) above; or
        by two or more persons falling within sub-paragraph (A), when taken
        together
      a body corporate in which –
            the director or any connected person falling within paragraphs (i) to (iii) has a substantial interest; or
            two or more persons falling within sub-paragraph (A) who, when
            taken together, have a substantial interest.
    For the purposes of interpreting the terms used in sub-clauses \ref{def-charity}
    and \ref{def-connected}, paragraphs 2 to 4 of Schedule 5 to the Charities Act 1993
    apply.

@@

\item
  \begin{enumerate}
  \item \label{dissolve-transfer}
    The members of the charity may at any time before, and in
    expectation of, its dissolution resolve that any net assets of the
    charity after all its debts and liabilities have been paid, or
    provision has been made for them, shall on or before the
    dissolution of the charity be applied or transferred in any of the
    following ways:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any charity or charities for purposes similar to the
      Objects; or
    \item
      to any charity or charities for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    Subject to any such resolution of the members of the charity, the
    directors of the charity may at any time before and in expectation
    of its dissolution resolve that any net assets of the charity after
    all its debts and liabilities have been paid, or provision made for
    them, shall on or before dissolution of the charity be applied or
    transferred:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any charity or charities for purposes similar to the
      Objects; or
    \item
      to any charity or charities for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    In no circumstances shall the net assets of the charity be paid to
    or distributed among the members of the charity (except to a member
    that is itself a charity) and if no resolution in accordance with
    article \ref{dissolve-transfer} is passed by the members or the directors the net
    assets of the charity shall be applied for charitable purposes as
    directed by the Court or the Commission.
  \end{enumerate}
\end{enumerate}

>>>>

\item
  The charity's objects (``Objects'') are specifically restricted to
  the following:
  \begin{enumerate}
  \item
    to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
  \item
    to provide and maintain shared community workspace and equipment in Greater London.
  \end{enumerate}

@@

\item
  \label{cls:income-property}
  \begin{enumerate}
  \item
    The income and property of the charity shall be applied solely
    towards the promotion of the Objects.
  \item
    \label{scls:director-reimburse}
    \begin{enumerate}
    \item
      A director is entitled to be reimbursed from the property of the
      charity or may pay out of such property reasonable expenses
      properly incurred by him or her when acting on behalf of the
      charity.
    \item
      A director may benefit from trustee indemnity insurance cover
      purchased at the charity's expense in accordance with, and subject
      to the conditions in, section 73F of the Charities Act 1993.
    \item
      A director may receive an indemnity from the charity in the
      circumstances specified in article \ref{cls:directors-indemnity}.
    \end{enumerate}
  \item
    Subject to article \ref{cls:benefits-payments}, none of the income or 
    property of the charity may be paid or
    transferred directly or indirectly by way of dividend bonus or
    otherwise by way of profit to any member of the charity. This does
    not prevent a member who is not also a director receiving:
    \begin{enumerate}
    \item
      a benefit from the charity in the capacity of a beneficiary of the
      charity;
    \item
      reasonable and proper remuneration for any goods or services
      supplied to the charity.
    \end{enumerate}
  \end{enumerate}

\section{Benefits and Payments to Charity Directors and Connected Persons}

\item
  \subsection{General provisions}
  \label{cls:benefits-payments}
  \begin{enumerate}
  \item
    \label{scls:directors-remuneration} No director or connected person
    may:
    \begin{enumerate}
    \item
      buy any goods or services from the charity on terms preferential to
      those applicable to members of the public;
    \item
      sell goods, services, or any interest in land to the charity;
    \item
      be employed by, or receive any remuneration from, the charity;
    \item
      receive any other financial benefit from the charity; unless:
      \begin{enumerate}
      \item
        the payment is permitted by article \ref{scls:directors-scope}; or
      \item
        the directors obtain the prior written approval of the Commission
        and fully comply with any procedures it prescribes. 
      \end{enumerate}
        In this article
        a `financial benefit' means a benefit, direct or indirect, which is
        either money or has a monetary value.
    \end{enumerate}

@@

    \subsection{Scope and powers permitting directors’ or connected persons’ benefits}

@@

      A director or connected person may take part in the
      normal trading and fundraising activities of the charity on
      the same terms as members of the public.

@@

    \subsection{Payment for supply of goods only – controls}
    \label{goods}

@@

    In sub-clauses \ref{scls:directors-scope} to \ref{goods}, ``charity'' shall include

@@

@@

\item
  \begin{enumerate}
  \item \label{dissolve-transfer}
    The members of the charity may at any time before, and in
    expectation of, its dissolution resolve that any net assets of the
    charity after all its debts and liabilities have been paid, or
    provision has been made for them, shall on or before the
    dissolution of the charity be applied or transferred in any of the
    following ways:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any charity or charities for purposes similar to the
      Objects; or
    \item
      to any charity or charities for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    Subject to any such resolution of the members of the charity, the
    directors of the charity may at any time before and in expectation
    of its dissolution resolve that any net assets of the charity after
    all its debts and liabilities have been paid, or provision made for
    them, shall on or before dissolution of the charity be applied or
    transferred:
    \begin{enumerate}
    \item
      directly for the Objects; or
    \item
      by transfer to any charity or charities for purposes similar to the
      Objects; or
    \item
      to any charity or charities for use for particular purposes that
      fall within the Objects.
    \end{enumerate}
  \item
    In no circumstances shall the net assets of the charity be paid to
    or distributed among the members of the charity (except to a member
    that is itself a charity) and if no resolution in accordance with
    article \ref{dissolve-transfer} is passed by the members or the directors the net
    assets of the charity shall be applied for charitable purposes as
    directed by the Court or the Commission.
  \end{enumerate}

\item \label{def-connected}
    In articles \ref{cls:benefits-payments}, \ref{conflict-interest-loyalty},
    and \ref{directors-validity-void} ``connected person'' means:
    \begin{enumerate}
    \item
      \label{art:connected-child} a child, parent, grandchild,
      grandparent, brother or sister of the director;
    \item
      \label{art:connected-spouse} the spouse or civil partner of the
      director or of any person falling within paragraph (a) above;
    \item
      \label{art:connected-business} a person carrying on business in
      partnership with the director or with any person falling within
      paragraph (a) or (b) above;
    \item
      an institution which is controlled –
      \begin{enumerate}
      \item
        by the director or any connected person falling within paragraph (a) to (c) above; or
      \item
        by two or more persons falling within sub-paragraph (i), when taken
        together
      \end{enumerate}
    \item
      a body corporate in which –
      \begin{enumerate}
        \item
            the director or any connected person falling within paragraphs (a) to (c) has a substantial interest; or
        \item
            two or more persons falling within sub-paragraph (i) who, when
            taken together, have a substantial interest.
        \item
            Paragraphs 2 to 4 of Schedule 5 to the Charities Act 1993 apply for the
            purposes of interpreting the terms used in this sub-clause.
        \end{enumerate}
    \end{enumerate}
\end{enumerate}
